Evaluating Open Information Extraction for Ontologization of a Thematic Domain

### 2014-07-18 paper/ekaw-2014/ekaw2014.tex
shrinking paper from 16 to 15 pages, underway!

\subsection{ReVerb \& OpenIE 4.0}
For demonstrating our evaluation framework, we choose two state-of-the-art OIE systems: ReVerb~\cite{Fader2011a} and OpenIE 4.0~\cite{Mausam2012a}, which are shown to have outperformed the earlier systems such as TextRunner~\cite{Etzioni2008a}, $woe^{pos}$ and $woe^{parse}$~\cite{Wu2010a}. ReVerb addresses the issue of incoherent and uninformative extractions\footnote{We have used the terms \textit{assertions} and \textit{extractions} analogously.} found with the former systems, by using few syntactic and lexical constraints. OLLIE~\cite{Mausam2012a} is a successor of ReVerb, and includes the noun-mediated relations which are not handled by the latter. It also incorporates the context of the assertions in the form n-ary relations. OpenIE 4.0 employs a similar methodology to that of OLLIE, to retrieve assertions using semantic role labeling, also known as shallow semantic parsing. The implementations for both ReVerb and OpenIE 4.0 are available online\footnote{Available at https://github.com/knowitall/}.

\subsection{Semantic parsing}
On the other hand, deep semantic parsing is an active research topic in the natural language processing (NLP) community, which aims to obtain a complete logical form of a given sentence. It is used in applications such as question-answering systems, robotic navigation and further has several direct implications for OIE as it is domain-independent and is shown to be web-scalable~\cite{Harrington2007}. To our knowledge, there is no existing literature that compares semantic parsing with the likes of ReVerb and OpenIE 4.0. We therefore built an information extraction wrapper around a state-of-the-art semantic parser and compare with the selected OIE systems. What follows is a brief description of this system.

@@

\subsection{Text corpus}
Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Pages from the parent categories corresponding to both music traditions are obtained recursively. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to reduce the number of malformed and highly complex sentences. In the semantic parsing based system, to address the multiword named entities, we identify consecutive NNPs and merge them into one in a pre-processing step. In ReVerb and OpenIE4.0, they are handled in their respective implementations.

@@

\subsection{Gold standard}
We use the ontologies manually engineered with the help of domain experts (one musicologist and three musicians) as groundtruth for the evaluation in the tasks of concept identification and semantic relation extraction\footnote{Available at https://github.com/gopalkoduri/ontologies}. The concepts and relation-types used in our evaluation framework belong to the top most level in the ontologies and are agreed upon by all the experts. The groundtruth for entities for each concept correspond to the page-titles in the respective subcategory in the Wikipedia (eg: Carnatic\_musicians).

@@

\subsubsection{Concept identification.} It is the task of identifying the concepts in the domain. Objects from all the triples featuring a subsumption relation phrase are collected. They are disambiguated based on their spellings, mostly automatically using string matching and edit distance measures\footnote{Available at https://github.com/gopalkoduri/string-matching} with minimal manual intervention where necessary. The resulting objects are taken to be the candidate concepts of the given domain. We compare the coverage of these against the concepts\footnote{The term concept is used analogous to the term class in ontologies.} in the manually built ontologies.

\subsubsection{Entity identification.} It concerns with finding the entities of a given domain and assigning a concept to them. The set of subjects from all the triples are considered as candidates entities in the domain. A list of titles of the Wikpedia pages in the domain along with the categories each page belong to, is acquired. The page titles correspond to entities, and the categories are manually mapped to concepts in our ontology. This constitutes the reference with which we compare the results from the two subtasks of entity identification.

@@

\subsubsection{Semantic relation extraction.} It refers to the relation types other than those which convey concept hierarchies. The assertion shown in Fig.~\ref{fig:ccg_sample} is one such example, where \textit{plays} is a relation that connects \textit{person} and \textit{musical instrument} concepts. We compare the OIE systems in this task by two measures: breadth and depth of the identified relation types. Breadth corresponds to the absolute number of valid relation types identified for each concept, and the depth corresponds to the number of assertions for a given relation type that consist of the identified entities. The valid relation types are manually marked from among the relation phrases in the assertions.
\afterpage{
\begin{figure}[t]
\begin{center}
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-sentence.pdf}
		 \label{fig:quant-carnatic-sentences}
        }% 
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-argument.pdf}
		 \label{fig:quant-carnatic-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-reltype.pdf}
		 \label{fig:quant-carnatic-reltype}
        }% 
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-class.pdf}
		 \label{fig:quant-carnatic-concept}
        }% 
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Carnatic music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-carnatic}
\end{figure}
}

\afterpage{
\begin{figure}[t]
\begin{center} 
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-sentence.pdf}
		 \label{fig:quant-hindustani-sentences}
        }%
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-argument.pdf}
		 \label{fig:quant-hindustani-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-reltype.pdf}
		 \label{fig:quant-hindustani-reltype}
		}%
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-class.pdf}
		 \label{fig:quant-hindustani-concept}
        }%
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Hindustani music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-hindustani}
\end{figure}
}

@@

\paragraph{Concept identification.}
Recall that we define candidate concepts to be the collection of objects from the triples with subsumption relation type. We map these to the concepts in the ontologies as described in sec.~\ref{sec:framework}. Table.~\ref{tab:concept_identification} shows the number of concepts in the ontolgies for each music, and the number of concepts mapped from the assertions of the OIE systems. These results are consistent with our earlier observations of the results shown in figs.~\ref{fig:quant-carnatic-concept} and~\ref{fig:quant-hindustani-concept}.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Ontology} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 53 & 4 & 4 & 22 \\
  Hindustani  & 55 & 1 & 2 & 9 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of concepts in the ontologies for each music, and those mapped from the assertions of the OIE systems.}
\label{tab:concept_identification}
\end{table}

@@

\paragraph{Entity identification.}
The first subtask in this part is to find the entities in the domain. The candidate entities from each OIE system are defined to be the collection of subjects from all its triples. Table.~\ref{tab:object_identification} shows the total number of entities in the reference data taken from Wikipedia for each music, and the number of entities in the intersection of these with the candidate entities of each OIE system. There is no marked difference between the results, with nearly all the systems having about 60\% of the entities from reference data in their assertions. However, it is observed that these correspond to only about 7\% of all the possible candidate entities.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Reference} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 618 & 349 & 364 & 364 \\
  Hindustani  & 697 & 396 & 410 & 399 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of entities in the reference data for each music, and those identified using the OIE systems.}
\label{tab:object_identification}
\end{table}

@@

\paragraph{Semantic relation extraction.}
For the purpose of this task, the subsumption relation types and also those relation phrases which do not have a consistent meaning across the assertions were discarded. Then, following the procedure discussed in sec.\ref{sec:framework}, we have marked the valid relation types for each concept, and obtained the corresponding assertions featuring the entities in the domain. Table.~\ref{tab:qual-semantic-relex} shows the results, for both Carnatic and Hindustani music.

@@

\paragraph{\textbf{Acknowledgments.}} This research was partly funded by the European Research Council under the European Union's Seventh Framework Program, as part of the CompMusic project (ERC grant agreement 267583).

>>>>

\medskip
\noindent
\textbf{ReVerb \& OpenIE 4.0:}
For demonstrating our evaluation framework, we choose two state-of-the-art OIE systems: ReVerb~\cite{Fader2011a} and OpenIE 4.0~\cite{Mausam2012a}, which are shown to have outperformed the earlier systems such as TextRunner~\cite{Etzioni2008a}, $woe^{pos}$ and $woe^{parse}$~\cite{Wu2010a}. ReVerb addresses the issue of incoherent and uninformative extractions\footnote{We have used the terms \textit{assertions} and \textit{extractions} analogously.} found with the former systems, by using few syntactic and lexical constraints. OLLIE~\cite{Mausam2012a} is a successor of ReVerb, and includes the noun-mediated relations which are not handled by the latter. It also incorporates the context of the assertions in the form n-ary relations. OpenIE 4.0 employs a similar methodology to that of OLLIE, to retrieve assertions using semantic role labeling, also known as shallow semantic parsing. The implementations for both ReVerb and OpenIE 4.0 are available online\footnote{Available at https://github.com/knowitall/}.

\medskip
\noindent
\textbf{Semantic parsing:}
On the other hand, deep semantic parsing is an active research topic in the natural language processing (NLP) community, which aims to obtain a complete logical form of a given sentence. It is used in applications such as question-answering systems, robotic navigation and further has several direct implications for OIE as it is domain-independent and is shown to be web-scalable~\cite{Harrington2007}. To our knowledge, there is no existing literature that compares semantic parsing with the likes of ReVerb and OpenIE 4.0. We therefore built an information extraction wrapper around a state-of-the-art semantic parser and compare with the selected OIE systems. What follows is a brief description of this system.

@@

\medskip
\noindent
\textbf{Text corpus:} Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Pages from the parent categories corresponding to both music traditions are obtained recursively. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to reduce the number of malformed and highly complex sentences. In the semantic parsing based system, to address the multiword named entities, we identify consecutive NNPs and merge them into one in a pre-processing step. In ReVerb and OpenIE4.0, they are handled in their respective implementations.

@@

\medskip
\noindent
\textbf{Gold standard:} We use the ontologies manually engineered with the help of domain experts (one musicologist and three musicians) as groundtruth for the evaluation in the tasks of concept identification and semantic relation extraction\footnote{Available at https://github.com/gopalkoduri/ontologies}. The concepts and relation-types used in our evaluation framework belong to the top most level in the ontologies and are agreed upon by all the experts. The groundtruth for entities for each concept correspond to the page-titles in the respective subcategory in the Wikipedia (eg: Carnatic\_musicians).

@@

\medskip
\noindent
\textbf{Concept identification.} It is the task of identifying the concepts in the domain. Objects from all the triples featuring a subsumption relation phrase are collected. They are disambiguated based on their spellings, mostly automatically using string matching and edit distance measures\footnote{Available at https://github.com/gopalkoduri/string-matching} with minimal manual intervention where necessary. The resulting objects are taken to be the candidate concepts of the given domain. We compare the coverage of these against the concepts\footnote{The term concept is used analogous to the term class in ontologies.} in the manually built ontologies.

\medskip
\noindent
\textbf{Entity identification.} It concerns with finding the entities of a given domain and assigning a concept to them. The set of subjects from all the triples are considered as candidates entities in the domain. A list of titles of the Wikpedia pages in the domain along with the categories each page belong to, is acquired. The page titles correspond to entities, and the categories are manually mapped to concepts in our ontology. This constitutes the reference with which we compare the results from the two subtasks of entity identification.

@@

\medskip
\noindent
\textbf{Semantic relation extraction.} It refers to the relation types other than those which convey concept hierarchies. The assertion shown in Fig.~\ref{fig:ccg_sample} is one such example, where \textit{plays} is a relation that connects \textit{person} and \textit{musical instrument} concepts. We compare the OIE systems in this task by two measures: breadth and depth of the identified relation types. Breadth corresponds to the absolute number of valid relation types identified for each concept, and the depth corresponds to the number of assertions for a given relation type that consist of the identified entities. The valid relation types are manually marked from among the relation phrases in the assertions.
\afterpage{
\begin{figure}[t]
\begin{center}
        \subfigure[][Sentences]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-sentence.pdf}
		 \label{fig:quant-carnatic-sentences}
        }% 
        \qquad
        \subfigure[][Objects]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-argument.pdf}
		 \label{fig:quant-carnatic-object}
        }%
        \\
        \subfigure[][Relation types]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-reltype.pdf}
		 \label{fig:quant-carnatic-reltype}
        }% 
        \qquad
        \subfigure[][Concepts]{%
		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/carnatic_music/extrations-per-class.pdf}
		 \label{fig:quant-carnatic-concept}
        }% 
\end{center}
\caption{Distribution of no. of extractions from OIE systems for Carnatic music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
\label{fig:quant-carnatic}
\end{figure}
}

%\afterpage{
%\begin{figure}[t]
%\begin{center} 
%        \subfigure[][Sentences]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-sentence.pdf}
%		 \label{fig:quant-hindustani-sentences}
%        }%
%        \qquad
%        \subfigure[][Objects]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-argument.pdf}
%		 \label{fig:quant-hindustani-object}
%        }%
%        \\
%        \subfigure[][Relation types]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-reltype.pdf}
%		 \label{fig:quant-hindustani-reltype}
%		}%
%        \qquad
%        \subfigure[][Concepts]{%
%		 \includegraphics[width=0.45\linewidth]{../../data/results/quantitative/hindustani_music/extrations-per-class.pdf}
%		 \label{fig:quant-hindustani-concept}
%        }%
%\end{center}
%\caption{Distribution of no. of extractions from OIE systems for Hindustani music shown along different \textit{aspects}. For a given number of extractions on x-axis, the y-axis shows the logarithmic count of the instances in the \textit{aspect}, which have at least those many extractions.}
%\label{fig:quant-hindustani}
%\end{figure}
%}

@@

\medskip
\noindent
\textbf{Concept identification.}
Recall that we define candidate concepts to be the collection of objects from the triples with subsumption relation type. We map these to the concepts in the ontologies as described in sec.~\ref{sec:framework}. Table.~\ref{tab:concept_identification} shows the number of concepts in the ontolgies for each music, and the number of concepts mapped from the assertions of the OIE systems. These results are consistent with our earlier observations of the results shown in figs.~\ref{fig:quant-carnatic-concept} and~\ref{fig:quant-hindustani-concept}.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Ontology} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 53 & 4 & 4 & 22 \\
  Hindustani  & 55 & 1 & 2 & 9 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of concepts in the ontologies for each music, and those mapped from the assertions of the OIE systems.}
\label{tab:concept_identification}
\end{table}

@@

\medskip
\noindent
\textbf{Entity identification.}
The first subtask in this part is to find the entities in the domain. The candidate entities from each OIE system are defined to be the collection of subjects from all its triples. Table.~\ref{tab:object_identification} shows the total number of entities in the reference data taken from Wikipedia for each music, and the number of entities in the intersection of these with the candidate entities of each OIE system. There is no marked difference between the results, with nearly all the systems having about 60\% of the entities from reference data in their assertions. However, it is observed that these correspond to only about 7\% of all the possible candidate entities.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Reference} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 618 & 349 & 364 & 364 \\
  Hindustani  & 697 & 396 & 410 & 399 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of entities in the reference data for each music, and those identified using the OIE systems.}
\label{tab:object_identification}
\end{table}

@@

\medskip
\noindent
\textbf{Semantic relation extraction.}
For the purpose of this task, the subsumption relation types and also those relation phrases which do not have a consistent meaning across the assertions were discarded. Then, following the procedure discussed in sec.\ref{sec:framework}, we have marked the valid relation types for each concept, and obtained the corresponding assertions featuring the entities in the domain. Table.~\ref{tab:qual-semantic-relex} shows the results, for both Carnatic and Hindustani music.

@@

\medskip
\noindent
\textbf{Acknowledgments.} This research was partly funded by the European Research Council under the European Union's Seventh Framework Program, as part of the CompMusic project (ERC grant agreement 267583).
